### 2016-09-30 Theorem1_FP.tex
Syntax consistency of proofs 1 and 2
Syntax consistency

%F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x \rangle) \bmod m
\begin{proof}[\Cref{thm1}]
The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}. $\game{0}(A)$ exactly simulates $\ExpCorrect{\Pi_\mathrm{lin},\distr{\calS}{},r}{A}$ with hash functions $h_j(x) =  F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x \rangle) \bmod m$. So,

\begin{equation}
\AdvCorrect{\Pi_{\mathrm{lin}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
\end{equation}

@@

Recall that adversary~$A$ wins $\ExpCorrect{\Pi_{\mathrm{lin}},\distr{\calS}{},r}{}$ by finding~$r$ false positives. We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive. % We can also assume that every point in $\calZ$ has already been queried to $\Test$.  This latter assumption is not without loss, but can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$. 
%
%Under these assumptions,
So, if $\game{4}(A)=1$, then there is a zero-query adversary~$D$ that finds~$r$ false positives against $\tilde{\Pi}_{\mathrm{lin}}$, which is $\Pi_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.  We give this~$D$ in \Cref{fig:D}. Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives; it simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ FP's. It must be noted that, by the no-pointless queries assumption and the fact that the hash functions in $D$ are instantiated with random functions, $\pubaux$ is information theoretically independent of elements not in $S$. Thus we have
$\Prob{\game{4}(A)=1} =\Prob{\ExpCorrect{\tilde{\Pi}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}$.

Note that $\tilde{\Pi}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).  Kirsch and Mitzenmacher~\cite{KM} show that the upperbound on false-positive probability for a zero-query adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.  For $r>1$, we observe that~$A$'s queries $x_1,x_2,\ldots,x_q$ are distinct and not elements of the original set~$S$, since we assume no pointless queries. Let $\calF_i$ be the event that~$x_i(i \in \mathcal{I})$ is a false positive.  Since $\game{4}$ (equivalently $\tilde{\Pi}_{\mathrm{lin}}$) use independent random functions, the events $\calF_1,\calF_2,\ldots,\calF_r$ are independent. 
\[
\Prob{\ExpCorrect{\tilde{\Pi}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
\]

To summarize, we have 
\[
\AdvCorrect{\Pi_{\mathrm{lin}},\distr{\calS}{},r}{A}  \leq  \AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} +\dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\]
which is the bound claimed in the theorem statement. %\hfill \qed

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.99}{
\hpagessl{.52}{.5}
{
\underline{\game{0}(A)}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then $\err \gets \err + 1$\\
Return~$a$\\
%
\oracle{$\HashOracle(x)$}\\
for $i = 1$ to $k$\\
\nudge $h_i(x) = F_{K}(\langle 1,x \rangle) + i\cdot F_{K}(\langle 2,x \rangle) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$K \getsr \calK$, $\rho \getsr \Func{\univ,[m]}$\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then $\err \gets \err + 1$\\
Return~$a$\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = F_{K}(\langle 1,x \rangle) + i \cdot \rho(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\fpage{.99}{
\hpagessl{.52}{.5}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then $\err \gets \err + 1$\\
Return~$a$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = \rho_1(x) + i \cdot \rho_2(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{{$\game{3}(A)$},\fbox{$\game{4}(A)$}}\\
$c\gets 0$, $\bad \gets \false$, $\err \gets 0$;  $\calC \gets \emptyset$\\
$S \getsr A$; $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$c \gets c+1$\\
$v \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $c \in \mathcal{I}$ and $v = \qry_x(S)$ then \\
\nudge $\bad \gets \true$ \\
if $c \not\in \mathcal{I}$ and $v \neq \qry_x(S)$ then \\
\nudge $\bad \gets \true$\\
if $v \neq \qry_x(S)$ then $\err \gets \err +1$\\
Return~$v$\\
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm1}: Game playing argument}\label{fig:Game}
\end{figure}

>>>>

%F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x \rangle) \bmod m
\begin{proof}[\Cref{thm1}]
The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}. $\game{0}(A)$ exactly simulates $\ExpCorrect{\setprim_\mathrm{lin},r}{A}$ with hash functions $h_j(x) =  F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x \rangle) \bmod m$. So,

\begin{equation}
\AdvCorrect{\setprim_{\mathrm{lin}},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
\end{equation}

@@

Recall that adversary~$A$ wins $\ExpCorrect{\setprim_{\mathrm{lin}},r}{}$ by finding~$r$ false positives. We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive. % We can also assume that every point in $\calZ$ has already been queried to $\Test$.  This latter assumption is not without loss, but can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$. 
%
%Under these assumptions,
So, if $\game{4}(A)=1$, then there is a zero-query adversary~$D$ that finds~$r$ false positives against $\tilde{\setprim}_{\mathrm{lin}}$, which is $\setprim_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.  We give this~$D$ in \Cref{fig:D}. Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives; it simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ FP's. It must be noted that, by the no-pointless queries assumption and the fact that the hash functions in $D$ are instantiated with random functions, $\pubaux$ is information theoretically independent of elements not in $S$. Thus we have
$\Prob{\game{4}(A)=1} =\Prob{\ExpCorrect{\tilde{\setprim}_{\mathrm{lin}},r}{D} = 1}$.

Note that $\tilde{\setprim}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).  Kirsch and Mitzenmacher~\cite{KM} show that the upperbound on false-positive probability for a zero-query adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.  For $r>1$, we observe that~$A$'s queries $x_1,x_2,\ldots,x_q$ are distinct and not elements of the original set~$S$, since we assume no pointless queries. Let $\calF_i$ be the event that~$x_i(i \in \mathcal{I})$ is a false positive.  Since $\game{4}$ (equivalently $\tilde{\setprim}_{\mathrm{lin}}$) use independent random functions, the events $\calF_1,\calF_2,\ldots,\calF_r$ are independent. 
\[
\Prob{\ExpCorrect{\tilde{\setprim}_{\mathrm{lin}},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
\]

To summarize, we have 
\[
\AdvCorrect{\setprim_{\mathrm{lin}},r}{A}  \leq  \AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} +\dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\]
which is the bound claimed in the theorem statement. %\hfill \qed

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.99}{
\hpagessl{.52}{.5}
{
\underline{\game{0}(A)}\\
$K \getsr \calK $\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then $\err \gets \err + 1$\\
Return~$a$\\
%
\oracle{$\HashOracle(x)$}\\
for $i = 1$ to $k$\\
\nudge $h_i(x) = F_{K}(\langle 1,x \rangle) + i\cdot F_{K}(\langle 2,x \rangle) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$K \getsr \calK $, $\rho \getsr \Func{\univ,[m]}$\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then $\err \gets \err + 1$\\
Return~$a$\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = F_{K}(\langle 1,x \rangle) + i \cdot \rho(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\fpage{.99}{
\hpagessl{.52}{.5}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then $\err \gets \err + 1$\\
Return~$a$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = \rho_1(x) + i \cdot \rho_2(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{{$\game{3}(A)$},\fbox{$\game{4}(A)$}}\\
$c\gets 0$, $\bad \gets \false$, $\err \gets 0$;  $\calC \gets \emptyset$\\
$S \getsr A$; $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\
%
\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$c \gets c+1$\\
$v \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $c \in \mathcal{I}$ and $v = \qry_x(S)$ then \\
\nudge $\bad \gets \true$ \\
if $c \not\in \mathcal{I}$ and $v \neq \qry_x(S)$ then \\
\nudge $\bad \gets \true$\\
if $v \neq \qry_x(S)$ then $\err \gets \err +1$\\
Return~$v$\\
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm1}: Game playing argument}\label{fig:Game}
\end{figure}

### 2016-09-30 Theorem2_FP.tex
Syntax consistency

\begin{proof}[\Cref{thm2}]
We use a game playing argument (shown in \Cref{fig:2TGame}) similar to \Cref{thm1} to prove this theorem. In \game{0}, adversary attacks the correctness game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{A}$.
\begin{equation}
\AdvCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A)=1}\label{eq:2T0}
\end{equation}

@@

In $\game{1}$, $A$ attacks a different filter $\tilde{\Pi}_\mathrm{ds}$, in which $F_K$ is replaced by a random function. $\game{2}$ and $\game{3}$ on the other hand use lazy sampling in $\Hash$ to select random values from $[m]$. It can be observed that, except  $\Hash$, $\game{2}$ and $\game{3}$ are identical to $\game{3}$ and $\game{4}$ of previous theorem. Since, $\Hash$ in all of these games returns random values, the analyses and intermediate results of \Cref{thm1} apply to this theorem as well. Therefore,
\begin{align*}
\Prob{\game{1}(A)=1} = \Prob{\game{2}(A)=1}\\
\Prob{\game{3}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{2}(A)=1}
\end{align*}

Let $D$ be a zero-query adversary (shown in \Cref{fig:D}) that finds ~$r$ false positives against $\tilde{\Pi}_{\mathrm{ds}}$. Using explanations from previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpCorrect{\tilde{\Pi}_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ game. So, 
\begin{equation*}
\AdvCorrect{\tilde{\Pi}_{\mathrm{ds}},\distr{\calS}{},r}{D} = \Prob{\game{3}(A) = 1}\label{eq:2T8}
\end{equation*}

Note that like $\tilde{\Pi}_{\mathrm{lin}}$, $\tilde{\Pi}_{\mathrm{ds}}$ is the scheme that is analyzed in the classical Bloom filter literature. So, for a zero-query adversary $D$ and $r=1$, the upper bound on false-positive probability of a classical Bloom filter applies to $\tilde{\Pi}_{\mathrm{ds}}$ as well. For $r > 1$, based on the assumption that $A$ makes no pointless queries, the queries made by $A$ are distinct and not elements of the original set $S$. Also, since $\game{3}$ uses independent random functions, the event of getting a false positive is independent of the index of the query. So,
\begin{equation*}
\AdvCorrect{\tilde{\Pi}_{\mathrm{ds}},\distr{\calS}{},r}{D} =   {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\end{equation*}
\noindent
To summarize, we have
\[
\AdvCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\]
which is the bound claimed in the theorem statement. %\hfill \qed

>>>>

\begin{proof}[\Cref{thm2}]
We use a game playing argument (shown in \Cref{fig:2TGame}) similar to \Cref{thm1} to prove this theorem. In \game{0}, adversary attacks the correctness game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\setprim_{\mathrm{ds}},r}{A}$.
\begin{equation}
\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} = \Prob{\game{0}(A)=1}\label{eq:2T0}
\end{equation}

@@

In $\game{1}$, $A$ attacks a different filter $\tilde{\setprim}_\mathrm{ds}$, in which $F_K$ is replaced by a random function. $\game{2}$ and $\game{3}$ on the other hand use lazy sampling in $\Hash$ to select random values from $[m]$. It can be observed that, except  $\Hash$, $\game{2}$ and $\game{3}$ are identical to $\game{3}$ and $\game{4}$ of previous theorem. Since, $\Hash$ in all of these games returns random values, the analyses and intermediate results of \Cref{thm1} apply to this theorem as well. Therefore,
\begin{align*}
\Prob{\game{1}(A)=1} = \Prob{\game{2}(A)=1}\\
\Prob{\game{3}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{2}(A)=1}
\end{align*}

Let $D$ be a zero-query adversary (shown in \Cref{fig:D}) that finds ~$r$ false positives against $\tilde{\setprim}_{\mathrm{ds}}$. Using explanations from previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{\cdot}$ game. So, 
\begin{equation*}
\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} = \Prob{\game{3}(A) = 1}\label{eq:2T8}
\end{equation*}

Note that like $\tilde{\setprim}_{\mathrm{lin}}$, $\tilde{\setprim}_{\mathrm{ds}}$ is the scheme that is analyzed in the classical Bloom filter literature. So, for a zero-query adversary $D$ and $r=1$, the upper bound on false-positive probability of a classical Bloom filter applies to $\tilde{\setprim}_{\mathrm{ds}}$ as well. For $r > 1$, based on the assumption that $A$ makes no pointless queries, the queries made by $A$ are distinct and not elements of the original set $S$. Also, since $\game{3}$ uses independent random functions, the event of getting a false positive is independent of the index of the query. So,
\begin{equation*}
\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} =   {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\end{equation*}
\noindent
To summarize, we have
\[
\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\]
which is the bound claimed in the theorem statement. %\hfill \qed

### 2016-09-30 TheoremGBF_correctness.tex
Syntax consistency

\heading{Garbled Bloom filter in random oracle model (ROM). }
Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (right side).  The following result shows,

\begin{theorem}\label{thm:gbf-correctness}
Fix $r=1$, $k,m,n>0$, and let $\Pi_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described. For any adversary~$A$ that makes a maximum of~$\dbinom{m}{k}$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A}  \geq   \left(1 - e^{-n/m^k}\right)^{nr} + \dfrac{1}{\dbinom{m}{k}-n-(q-1)} . \Big(1-\dfrac{n}{2^\lambda}\Big)
\]

@@

If $\epsilon$ is the event of finding $r=1$ error, $\Prob{\epsilon} = \AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} =  \Prob{\epsilon_{\fn}} + \Prob{\epsilon_{\fp}}$($\epsilon_{\fn}$ and $\epsilon_{\fp}$ are mutually independent) and hence 
\[
\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A}  \geq \left(1 - e^{-n/m^k}\right)^{nr} + \dfrac{1}{\dbinom{m}{k}-n-(q-1)} . \Big(1-\dfrac{n}{2^\lambda}\Big)
\]

>>>>

\heading{Garbled Bloom filter in random oracle model (ROM). }
Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\setprim_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (right side).  The following result shows,

\begin{theorem}\label{thm:gbf-correctness}
Fix $r=1$, $k,m,n>0$, and let $\setprim_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described. For any adversary~$A$ that makes a maximum of~$\dbinom{m}{k}$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{garb}},r}{A}  \geq   \left(1 - e^{-n/m^k}\right)^{nr} + \dfrac{1}{\dbinom{m}{k}-n-(q-1)} . \Big(1-\dfrac{n}{2^\lambda}\Big)
\]

@@

If $\epsilon$ is the event of finding $r=1$ error, $\Prob{\epsilon} = \AdvCorrect{\setprim_{\mathrm{garb}},r}{A} =  \Prob{\epsilon_{\fn}} + \Prob{\epsilon_{\fp}}$($\epsilon_{\fn}$ and $\epsilon_{\fp}$ are mutually independent) and hence 
\[
\AdvCorrect{\setprim_{\mathrm{garb}},r}{A}  \geq \left(1 - e^{-n/m^k}\right)^{nr} + \dfrac{1}{\dbinom{m}{k}-n-(q-1)} . \Big(1-\dfrac{n}{2^\lambda}\Big)
\]
